Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-09-30 prob.tex
prob.tex Updating interpretation and example...

\documentclass{article}
\usepackage[ backend=biber,sorting=none]{biblatex}
\bibliography{discreteGBKS}
\usepackage{fullpage}
\usepackage{url}
\usepackage{bbm}
\usepackage{bbold}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{array}
\usepackage{mathrsfs}
\usepackage[all]{xy}
\usepackage{amsmath}
\usepackage{wesa}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{verbatim}

@@

\begin{definition}~Given an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$:
\begin{itemize}
\item A \emph{core}\footnote{The core is also called a structure~\cite{Weichselberger2000}.}
of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \textrm{probability measure }\pmeas:\events\rightarrow[0,1]\middle|\forall E\in\events.\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\right\} $
\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}.
\item $\bar{\mu}$ is called \emph{convex}, \emph{2-monotone}, or\emph{
supermodular} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014,Grabisch2016}.\footnote{\yutsung{In order to simplify the discussion, let $l$ be the left-end
of an interval-valued probability measure~$\bar{\mu}$. Because of
equation~(\ref{eq:ClassicalInterval-valuedProbability-Complement}),
$\bar{\mu}$ is convex if and only if 
\begin{equation}
l\left(E_{1}\cup E_{2}\right)+l\left(E_{1}\cap E_{2}\right)\ge l\left(E_{1}\right)+l\left(E_{2}\right)\textrm{ ,}\label{eq:convex-game}
\end{equation}
which is a special case of the Dempster-Shafer condition
\begin{equation}
l\left(\bigcup_{i=1}^{N}E_{i}\right)\ge\sum_{I\subseteq\left\{ 1,\ldots,N\right\} }\left(-1\right)^{\left|I\right|+1}l\left(\bigcap_{i\in I}E_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game}
\end{equation}
Therefore, in order to understand the meaning of equation~(\ref{eq:convex-game}),
we could try to understand meaning of the Dempster-Shafer belief function.
Unfortunately, when people introduce the Dempster-Shafer theory, they
usually don't start from equation~(\ref{eq:Dempster-Shafer-game}).
Instead, they introduce a basic belief assignment~$m\left(E\right)=\sum_{E'\subseteq E}\left(-1\right)^{\left|E\setminus E'\right|}l\left(E'\right)$
first, and $m\left(E\right)$ expresses the proportion of all relevant
and available evidence that supports the claim that the actual state
belongs to $A$ but to no particular subset of $A$. Then, equation~(\ref{eq:Dempster-Shafer-game})
is equivalent to $m\left(E\right)\ge0$ for all $E$~\cite{Grabisch2016},
and the later statement is intuitive.}}
\end{itemize}
\qed\end{definition}

@@

Recall that when approximating the probability classically, the quality
of the experimental equipment cannot be compensated by the number
of independent trials. If the precision of the intervals~$\mathscr{I}$
represents the quality of the quantum experimental equipment, example~\ref{ex:three-dimensional-three-value}
tells us that we cannot identify a particular state if the experimental
equipment reveals too little information.

If we examine our examples more carefully, we find that example~\ref{ex:three-dimensional-three-value}
really use the property of $\unknown$ so that it cannot hold when
the intervals are more precise; example~\ref{ex:three-dimensional-4-value}
also cannot work with any interval values more precise than $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $.
Also, example~\ref{ex:three-dimensional-4-value} is not as bad as
example~\ref{ex:three-dimensional-three-value} in a sense that the
$\imposs$ states are all in the same plane in example~\ref{ex:three-dimensional-4-value}
while the $\imposs$ states are not in the same plane in example~\ref{ex:three-dimensional-4-value}.
Maybe interval-valued probability measures will be closer and closer
to real-valued probability measures if the intervals are more and
more precise?

@@

\section{Examples for Quantum Interval-valued Probability Measures}

We are going to provide an quantum 4-value interval-valued probability
measures corresponding to no quantum probability measure, i.e., for
all mixed state~$\rho$ there is a $P\in\events$ such that $\mu_{\rho}^{B}(P)\notin\bar{\mu}(P)$.

@@

\begin{eqnarray*}

@@

\end{eqnarray*}

@@

\end{eqnarray*}

@@

\begin{eqnarray*}
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right)=\likely & \subseteq & \unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{3}}\right)
\end{eqnarray*}

>>>>

\documentclass{article}
\usepackage[ backend=biber,sorting=none,maxbibnames=5]{biblatex}
\bibliography{discreteGBKS}
\usepackage{fullpage}
\usepackage{url}
\usepackage{bbm}
\usepackage{bbold}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{array}
\usepackage{mathrsfs}
\usepackage[all]{xy}
\usepackage{amsmath}
\usepackage{wesa}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{verbatim}

@@

\begin{definition}~Given an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$:
\begin{itemize}
\item A \emph{core}\footnote{The core is also called a structure~\cite{Weichselberger2000}.}
of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \textrm{probability measure }\pmeas:\events\rightarrow[0,1]\middle|\forall E\in\events.\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\right\} $
\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}.
\item $\bar{\mu}$ is called \emph{convex}, \emph{2-monotone}, or\emph{
supermodular} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014,Grabisch2016}.\footnote{\yutsung{In order to simplify the discussion, let $l$ be the left-end
of an interval-valued probability measure~$\bar{\mu}$. Because of
equation~(\ref{eq:ClassicalInterval-valuedProbability-Complement}),
$\bar{\mu}$ is convex if and only if 
\begin{equation}
l\left(E_{1}\cup E_{2}\right)+l\left(E_{1}\cap E_{2}\right)\ge l\left(E_{1}\right)+l\left(E_{2}\right)\textrm{ ,}\label{eq:convex-game}
\end{equation}
which is a special case of the Dempster-Shafer condition
\begin{equation}
l\left(\bigcup_{i=1}^{N}E_{i}\right)\ge\sum_{I\subseteq\left\{ 1,\ldots,N\right\} }\left(-1\right)^{\left|I\right|+1}l\left(\bigcap_{i\in I}E_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game}
\end{equation}
Therefore, in order to understand the meaning of equation~(\ref{eq:convex-game}),
we could try to understand meaning of the Dempster-Shafer belief function.
Unfortunately, when people introduce the Dempster-Shafer theory, they
usually don't start from equation~(\ref{eq:Dempster-Shafer-game}).
Instead, they introduce a basic belief assignment~$m\left(E\right)=\sum_{E'\subseteq E}\left(-1\right)^{\left|E\setminus E'\right|}l\left(E'\right)$
first, and $m\left(E\right)$ represents the belief committed to the
event~$E$ and only to it, in the sense that it could not be committed
to any proper subset of $A$~\cite{Grabisch2016}. Then, equation~(\ref{eq:Dempster-Shafer-game})
is equivalent to $m\left(E\right)\ge0$ for all $E$~\cite{Grabisch2016},
and the non-negative of $m\left(E\right)$ is intuitive.

Comparing to the Dempster-Shafer condition~\ref{eq:Dempster-Shafer-game},
the equivalent condition for convexity is more complex. At least,
when $l$ is convex, we have 
\begin{equation}
m\left(\left\{ \omega_{0},\omega_{1}\right\} \right)\ge0\label{eq:convex-positive}
\end{equation}
 for all $\left\{ \omega_{0},\omega_{1}\right\} \subseteq\Omega$,
although equation~(\ref{eq:convex-positive}) is not strong enough
to imply $l$ is convex.}}
\end{itemize}
\qed\end{definition}

@@

Recall that when approximating the probability classically, the quality
of the experimental equipment cannot be compensated by the number
of independent trials. If the precision of the intervals~$\mathscr{I}$
represents the quality of the quantum experimental equipment, example~\ref{ex:three-dimensional-three-value}
tells us that we cannot identify a particular state if the experimental
equipment reveals too little information. For example, $\bar{\mu}$
might correspond to $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
$\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$,
or the density matrix~$\frac{\mathbb{1}}{3}$ because $\bar{\mu}(\proj{\phi})\ne\necess$
for all $\ket{\phi}$. Also, example~\ref{ex:three-dimensional-three-value}
is no longer valid if our measurement equipment is a little more precise,
say $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
because example~\ref{ex:three-dimensional-three-value} really use
the property of $\unknown$.

If we consider $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
example~\ref{ex:three-dimensional-4-value} in appendix~\ref{sec:Examples-for-QuantumIVPM}
provides another example with an empty core. Comparing to example~\ref{ex:three-dimensional-three-value},
example~\ref{ex:three-dimensional-4-value} is closer to the Born
rule in a sense that it might only correspond to $\ket{2}$ or $\frac{\mathbb{1}}{3}$,
but not $\ket{1}$, and it is no longer valid for more precise measurement
equipment as well. In general, we believe if the measurement equipment
is more and more precise, its interval-valued probability measure
will be closer and closer to the the Born rule. In the limit case,
$\mathscr{I}=\left\{ \left\{ a\right\} \middle|a\in\left[0,1\right]\right\} $
recovers conventional Gleason's theorem and the Born rule.

@@

\section{\label{sec:Examples-for-QuantumIVPM}Examples for Quantum Interval-valued
Probability Measures}

We are going to provide an quantum 4-value interval-valued probability
measures corresponding to no quantum probability measure, i.e., for
all mixed state~$\rho$ there is a $P\in\events$ such that $\mu_{\rho}^{B}(P)\notin\bar{\mu}(P)$.
After the example, we will also justify why this example cannot fit
with more precise intervals.

@@

\begin{equation}
\begin{array}{rcl}

@@

\end{array}\label{eq:case1}
\end{equation}

@@

\end{array}\label{eq:case2}
\end{equation}

@@

\begin{equation}
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right)=\likely\subseteq\unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{3}}\right)\label{eq:case3}
\end{equation}
